---
title: "PS811 Portfolio"
author: "Sam Schutt"
output:
  html_document:
    code_folding: hide
    toc: yes
  pdf_document:
    toc: yes
---
```{r setup, include=FALSE}
## Defaults for R chunks
knitr::opts_chunk$set(echo = TRUE, ## echo = TRUE means code will show
                      warning=FALSE, ## supress warnings and messages from R
                      message=FALSE,
                      fig.path='Figs/', ## where to save figures
                      fig.height = 3, ## default figure size (can differ in each chunk)
                      fig.width = 3)

## Add any R packages you require. 
## Here are some we will use in 811:
requires <- c("tidyverse", ## tidyverse includes dplyr and ggplot2
              "magrittr",
              "foreign",
              "readstata13",
              "here")

## Install any you don't have
to_install <- c(requires %in% rownames(installed.packages()) == FALSE)
install.packages(c(requires[to_install], "NA"), repos = "https://cloud.r-project.org/" )

## Load all required R packages
library(tidyverse)
library(ggplot2); theme_set(theme_minimal())
library(magrittr)
library(here)
library(foreign)
library(haven)
```
<!-- The above header sets everything up. -->





<!-- Replace the below with bit about you. -->
### Research Interests
As an American Politics student, my interests are in the subfield of political psychology broadly. Less-broad topics of study that I see in my future are the connection between emotions and voting behavior, decision-making processes, religion, information processing, and elite psychology. Another topic that is less of a research focus, but more of hobby and consumer is rural resentment and white-working class voting behavior. 

### Current Research Project or Questions of Interest
How does anxiety affect information processing during elections? How does anxiety and depression affect voter turnout and vote choice? 

How do religion and anxiety interact to influence voter behavior?

How does anxiety for Presidential candidates affect congressional perception?

Anxiety and Correct Voting 

---

### Relevent data

- [American National Election Survey](https://electionstudies.org/)


---

###Summary of ANES
```{r anes data load}
load(here("data/anes2016anx.Rdata"))
d<-anes2016anx
```

```{r}
d<-mutate(d, anxietyD = ((angerD+ afraidD+ disgustD)/3))
d<-mutate(d, anxietyR = ((angerR + afraidR + disgustR)/3))
d<-mutate(d, enthD = ((proudD + hopefulD)/2))
d<-mutate(d, enthR = ((proudR + hopefulR)/2))
d
```

