---
title: "PS811 Portfolio"
author: "Sam Schutt"
output:
  html_document:
    code_folding: hide
    toc: yes
  pdf_document:
    toc: yes
---
```{r setup, include=FALSE}
## Defaults for R chunks
knitr::opts_chunk$set(echo = TRUE, ## echo = TRUE means code will show
                      warning=FALSE, ## supress warnings and messages from R
                      message=FALSE,
                      fig.path='Figs/', ## where to save figures
                      fig.height = 3, ## default figure size (can differ in each chunk)
                      fig.width = 3)

## Add any R packages you require. 
## Here are some we will use in 811:
requires <- c("tidyverse", ## tidyverse includes dplyr and ggplot2
              "magrittr",
              "foreign",
              "readstata13",
              "here")

## Install any you don't have
to_install <- c(requires %in% rownames(installed.packages()) == FALSE)
install.packages(c(requires[to_install], "NA"), repos = "https://cloud.r-project.org/" )

## Load all required R packages
library(tidyverse)
library(ggplot2); theme_set(theme_minimal())
library(magrittr)
library(here)
library(foreign)
library(haven)
```
<!-- The above header sets everything up. -->





<!-- Replace the below with bit about you. -->
### Research Interests
My focus is on Presidential elections, and more specifically on how emotions and mental health affect voting behavior. Other interests include purple state politics, correct voting, elite decision-making and state politics of Wisconsin.

### Questions I hope to answer
How does anxiety affect information processing during elections? How does anxiety and depression affect voter turnout and vote choice? 

How do religion and anxiety interact to influence voter behavior?

---

### Relevent data

- American National Election Survey


---

###Summary of ANES
```{r anes data load}
load(here("data/anes2016anx.Rdata"))
d<-anes2016anx
```

```{r}
d<-mutate(d, anxietyD = ((angerD+ afraidD+ disgustD)/3))
d<-mutate(d, anxietyR = ((angerR + afraidR + disgustR)/3))
d<-mutate(d, enthD = ((proudD + hopefulD)/2))
d<-mutate(d, enthR = ((proudR + hopefulR)/2))
d
```

